Model

### 2019-10-17 stats/model.Rmd
update model processing)

@@

#saveRDS(sem_know_model, "../saves/model1.rds")

sem_know_model <- readRDS("../saves/model1.rds")
```

## Model compatison

```{r}
log_like <- sem_know_model %>%
  separate(Parameter, into = c("parameter", "model","noise","alignment"), sep = ",")%>%
  filter(parameter == "log_like")%>%
  separate(value, into = c("na", "log_like"),sep = ",")%>%
  select(-na, -alignment)%>%
  mutate(log_like =as.numeric(str_remove(log_like,"[)]")))

log_like_chain<- sem_know_model %>%
  separate(Parameter, into = c("parameter", "model","noise","alignment"), sep = ",")%>%
  filter(parameter == "log_like")%>%
  separate(value, into = c("na", "log_like"),sep = ",")%>%
  select(-na, -alignment)%>%
  mutate(log_like =as.numeric(str_remove(log_like,"[)]")))%>%
  group_by(model,Chain, noise)%>%
  summarize(logP = logSumExp(log_like))%>%
  spread(noise, logP)

@@

model_pred <- sem_know_model %>%
  separate(Parameter, into = c("type", "model","parameter","alignment","item"))%>%
  filter(type == "modelPrediction")%>%
  separate(value, into = c("age", "pred"),sep = ", ")%>%
  mutate(age = as.numeric(str_remove_all(age, "[(c]")),
         pred = as.numeric(str_remove(pred, "[)]")))

item_params<- sem_know_model %>%
  separate(Parameter, into = c("parameter", "type","item"), sep = ",")%>%
  filter(parameter == "parameter", type == "items")%>%
  separate(value, into = c("int", "slope"),sep = ", ")%>%
  mutate(int = as.numeric(str_remove_all(int, "[(c]")),
         slope = as.numeric(str_remove(slope, "[)]")))%>%
  gather(parameter, value, int, slope)

global_params <- sem_know_model %>%
  separate(Parameter, into = c("parameter", "type","token"), sep = ",")%>%
  filter(parameter == "parameter", type == "parameters")%>%
    separate(value, into = c("int", "slope"),sep = ", ")%>%
    mutate(int = as.numeric(str_remove_all(int, "[(c]")),
         slope = as.numeric(str_remove(slope, "[)]")))%>%
    gather(parameter, value, int, slope)

global_sigma<- sem_know_model %>%
  separate(Parameter, into = c("parameter", "type","token"), sep = ",")%>%
  filter(parameter == "parameter", type == "sigma", token != "global_subject_sigmas")%>%
    separate(value, into = c("sigma_int", "sigma_slope"),sep = ", ")%>%
    mutate(sigma_int = as.numeric(str_remove_all(sigma_int, "[(c]")),
         sigma_slope = as.numeric(str_remove(sigma_slope, "[)]")))%>%
    gather(parameter, value, sigma_int, sigma_slope)

subj_sigma<- sem_know_model %>%
  separate(Parameter, into = c("parameter", "type","token"), sep = ",")%>%
  filter(parameter == "parameter", token == "global_subject_sigmas")%>%
  separate(value, into = c("na", "sigma"),sep = ", ")%>%
  select(-na)%>%
  mutate(sigma = as.numeric(str_remove(sigma, "[)]")))

subject_params<- sem_know_model %>%
  separate(Parameter, into = c("parameter", "type","id"), sep = ",")%>%
  filter(parameter == "parameter", type == "subj_intercept")%>%
  separate(value, into = c("na", "int"),sep = ", ")%>%
  select(-na)%>%
  mutate(int = as.numeric(str_remove(int, "[)]")))

model_pred<- sem_know_model %>%
  separate(Parameter, into = c("parameter", "item","age","alignment"), sep = ",")%>%
  filter(parameter == "prediction")%>%
  separate(value, into = c("na", "me_effect"),sep = ",")%>%
  select(-na)%>%
  mutate(age = as.numeric(age),
         me_effect =as.numeric(str_remove(me_effect,"[)]")))

@@

# model_pred_summary <- model_pred %>%
#   group_by(item,age)%>%
#   summarise(mode = estimate_mode(pred),
#             uci = hdi_upper(pred),
#             lci = hdi_lower(pred))

@@

```{r}
plot_item_params <- ggplot(item_params, aes(x = value, fill = factor(Chain)))+
  geom_density(alpha = 0.3)+
  xlab("Parameter")+
  facet_grid(parameter~item, scales = 'free')+
  theme_few()

@@

plot_global_params <- ggplot(global_params, aes(x = value, fill = factor(Chain)))+
  geom_density(alpha = 0.3)+
  xlab("Parameter")+
  facet_grid(parameter~token, scales = 'free')+
  theme_few()

@@

```{r}
plot_global_sigma <- ggplot(global_sigma, aes(x = value, fill = factor(Chain)))+
  geom_density(alpha = 0.3)+
  xlab("Sigma")+
  facet_grid(~parameter, scales = 'free')+
  theme_few()

@@

ggplot() +
  geom_hline(yintercept = 0.5, lty=2)+
  #geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "loess", se = T, alpha = .5, span = 2)+
  geom_line(data = plot_model_pred, aes(x=age+2,y = mean, col = model), size = 1)+
  geom_ribbon(data = plot_model_pred, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = model), alpha = .4) +
  labs(x="Age",y="Mutual Exclusivity effect")+
  facet_grid(alignment~item)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F, fill = F)+ 
  scale_colour_ptol(name = NULL)+
  scale_fill_ptol(name = NULL)
```

>>>>

data_comb_pre <- read_csv("../data/combination.csv")

aoa_ratings_all <- read_xlsx(path = "../data/words_aoa_ratings.xlsx", sheet = 1)

aoa_ratings <- aoa_ratings_all %>%
  filter(Word %in% data_comb_pre$item )%>%
  mutate(mean_aoa = as.numeric(Rating.Mean),
         item = Word)%>%
  select(item,mean_aoa)

data_comb <- data_comb_pre%>%
  filter(condition != "train")%>%
  mutate(alignment = condition,
         item = familiarObject)%>%
  left_join(aoa_ratings)%>%
  ungroup()%>%
  mutate(item = fct_reorder(factor(familiarObject), mean_aoa), 
         source = "Data")

@@

bind_rows(
sem_know_model <- read_csv("../saves/model/samples628.csv")%>%mutate(chain =1)
)

saveRDS(sem_know_model, "../saves/model_complete.rds")

sem_know_model <- readRDS("../saves/model_complete.rds")

```
## Model comparison

```{r}
log_like <- sem_know_model %>%
  filter(a == "log_like")%>%
  select(b,c,e)%>%
  rename(model = b, 
         parameter = c,
         log_like = e)

saveRDS(log_like, "../saves/log_like.rds")
log_like <- readRDS("../saves/log_like.rds")

log_like_model<- log_like %>%
  group_by(model,parameter)%>%
  summarize(logP = logSumExp(log_like))%>%
  spread(parameter, logP)

saveRDS(log_like_model, "../saves/log_like_model.rds")
log_like_model <- readRDS("../saves/log_like_model.rds")

log_like_chain<- log_like %>%
  group_by(chain, model,parameter)%>%
  summarize(logP = logSumExp(log_like))%>%
  spread(parameter, logP)

saveRDS(log_like_chain, "../saves/log_like_chain.rds")
log_like_chain <- readRDS("../saves/log_like_chain.rds")

@@

model_pred <- sem_know_model %>%
  filter(a == "modelPrediction")%>%
  select(-a, -f)%>%
  rename(model = b, 
         parameter = c,
         alignment = d,
         item = e,
         age = g, 
         pred = h)

saveRDS(model_pred, "../saves/model_pred.rds")
model_pred <- readRDS("../saves/model_pred.rds")

model_params<- sem_know_model %>%
  filter(a == "parameter")

saveRDS(model_params, "../saves/model_params.rds")
model_params <- readRDS("../saves/model_params.rds")

item_params <-  model_params %>%
  filter(b == "items")%>%
  select(-a,-b, -g,-h, -f)%>%
    rename(item = c,
         int = d,
         slope = e)%>%
  mutate(slope = as.numeric(slope),
         int = as.numeric(int))%>%
  gather(parameter, value, int, slope)

saveRDS(item_params, "../saves/item_params.rds")
item_params <- readRDS("../saves/item_params.rds")

global_params <- model_params %>%
  filter(b == "parameters")%>%
  select(-a,-b, -g,-h, -f)%>%
    rename(token = c,
         int = d,
         slope = e)%>%
  mutate(slope = as.numeric(slope),
         int = as.numeric(int))%>%
  gather(parameter, value, int, slope)

saveRDS(global_params, "../saves/global_params.rds")
global_params <- readRDS("../saves/global_params.rds")

global_sigma<- sem_know_model %>%
  filter(b == "sigma")%>%
  select(-a,-b, -g,-h, -f)%>%
    rename(token = c,
         int = d,
         slope = e)%>%
  mutate(slope = as.numeric(slope),
         int = as.numeric(int))%>%
  gather(parameter, value, int, slope)

saveRDS(global_sigma, "../saves/global_sigma.rds")
global_sigma <- readRDS("../saves/global_sigma.rds")

@@

@@

```{r}
plot_item_params <- ggplot(item_params, aes(x = value, fill = factor(chain)))+
  geom_density(alpha = 0.3)+
  xlab("Parameter")+
  facet_grid(parameter~item, scales = 'free')+
  theme_few()

@@

plot_global_params <- ggplot(global_params, aes(x = value, fill = factor(chain)))+
  geom_density(alpha = 0.3)+
  xlab("Parameter")+
  facet_grid(parameter~token, scales = 'free')+
  theme_few()

@@

```{r}
plot_global_sigma <- ggplot(global_sigma, aes(x = value, fill = factor(chain)))+
  geom_density(alpha = 0.3)+
  xlab("Sigma")+
  facet_grid(~parameter, scales = 'free')+
  theme_few()

@@

ggplot() +
  geom_hline(yintercept = 0.5, lty=2)+
  #geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "loess", se = T, alpha = .5, span = 2)+
  geom_line(data = plot_model_pred, aes(x=age+2,y = mean, col = model), size = 1)+
  geom_ribbon(data = plot_model_pred, aes(x = age+2, ymin = ci_lower, ymax = ci_upper, fill = model), alpha = .4) +
  labs(x="Age",y="Mutual Exclusivity effect")+
  facet_grid(model + alignment~item)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F, fill = F)+ 
  scale_colour_ptol(name = NULL)+
  scale_fill_ptol(name = NULL)
```
